Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-07 papers/main.tex
TEMPORARY DEPLOY COMMIT

\textcolor{red}{A natural step for finding
the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
between it and the true Q-value function. This is different from the optimization
scheme in NoisyNet, which only tries to maximize the likelihood that samples from
\(q_\phi\) comes from the true Q-value function.} \textcolor{green}{This should probably go under method}

We would like to approximate the posterior distribution of the Q value function.
This would (1) give optimal regret, (2) let us incorporate domain knowledge
through an appropriate prior distribution.
We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples
from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let

@@

\subsection{Informative Prior}

>>>>

\textcolor{red}{A natural step for finding
the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
between it and the true Q-value function. This is different from the optimization
scheme in NoisyNet, which only tries to maximize the likelihood that samples from
\(q_\phi\) comes from the true Q-value function.}

We would like to approximate the posterior distribution of the Q-value function.
This would (1) give optimal regret, (2) let us incorporate domain knowledge
through an appropriate prior distribution.
We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples
from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let

@@

\subsection{Informative Prior}
We will also look at how our method can utilize domain knowledge to improve sample efficiency. We will use the following method to calculate the prior distribution on the Q-values:

\textcolor{red}{Discuss how to go from policy prior to Q-value prior.}

\begin{figure}
    \includegraphics[width=\columnwidth]{example-image}
    \caption{Performance on the CartPole-v1 environment.}
\end{figure}
